Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-11 paper/ms.tex
Add action-orbit integration sentence
Just blow the intro up

We define the ``global Galactic midplane'' to be the plane of $z$ symmetry in
the axisymmetric model of the Milky Way. We define the ``local Galactic
midplane'' to be the plane of $z$ symmetry inferred by an observer at a
particular location. The true global Galactic midplane is the plane of $z$
symmetry in the best-fit axisymmetric model. It is not guaranteed that the
local Galactic midplane coincide with the global Galactic midplane. Even
without a high-precision definition and measurement of the global Galactic
midplane, we can still assess how different the two should be by measuring the
azimuthal dependence of the local Galactic midplane. This procedure may be
readily tractable with current datasets. However, we turn to simulation in
this work.

It's important for us to emphasize that when we state our local Galactic
midplane may be erroneous, we do not mean that past measurements/estimates of
it are wrong. Rather, what we mean is that it may vary from the local midplane
at other points in the Galaxy. In the face of {\em Gaia} DR2 (and soon DR3/4),
this may be an important effect to consider when performing dynamical
modelling across large distances.

@@

To provide a realization of a realistic Galactic potential, we turn to
cosmological zoom-ins of Milky Way-mass galaxies from the Feedback in
Realistic Environments (FIRE)
collaboration\footnote{\url{https://fire.northwestern.edu}} (the {\em Latte}
suite of simulations).

@@

>>>>

@@

We propose a new type of error in the computation of actions which has
implications for general dynamical modelling across the disk. Our main point
is that the ``local'' Galactic midplane is not the same as the ``global''
Galactic midplane. If we observe a group of stars that are
non-local\footnote{i.e. a group of stars that is far enough away. The exact
distance depends on the accuracy of the measurement being made and the goals
of the particular problem.}, they will know of a different local midplane than
our local midplane extrapolated onto their position. This means that when we
convert those star's positions and velocities from a heliocentric to a
Galactocentric coordinate system, we are inducing a systematic bias in those
stars' $z$ values. The same applies to inaccuracies in measurements of
$R_{\odot}$ and variations in the local standard of rest (LSR).

We do not propose what a modeller should use for the ``true'' global midplane,
since such a definition probably depends on the particular problem such a
modeller is facing. Even without a high-precision definition and measurement
of the global Galactic midplane, we can still assess how different we should
expect the local midplane to be by measuring the azimuthal dependence of the
local midplane. This procedure may be readily tractable over some of the disk
with current datasets. However, we turn to simulation in this work because we
can investigate the entire disk. Specifically, we use cosmological zoom-ins of
Milky Way-mass galaxies from the Feedback in Realistic Environments (FIRE)
collaboration\footnote{\url{https://fire.northwestern.edu}} (the {\em Latte}
suite of simulations).

It is important for us to emphasize that when we state our local Galactic
midplane may be erroneous, we do not mean that past measurements/estimates of
it are wrong. Rather, what we mean is that it may vary from the local midplane
at other points in the Galaxy. In the face of {\em Gaia} DR2 (and soon DR3/4),
this may be an important effect to consider when performing dynamical
modelling across large distances.

@@

While in this work we have focused on errors in action computation, all of our
conclusions also extend to studies of stars that simply rely on orbit
integration, since the computation of actions and orbit integrations are
essentially equivalent.
